### 2020-04-05 08-conclusion.tex
ultime modifiche

In this paper we have introduced a variant of the {\tt link}-calculus
where prefixes are link chains and no more single links, as it was 
briefly described in the future work section in~\cite{BBB17}.
This variant allowed us to define 
%shown 
a faithful embedding of Reaction Systems,
an emerging formalism to model computationally biochemical systems.
%into multilink processes.  
This translation shows several benefits.
For instance, in our paper the context works non deterministically and it 
is recursively defined.
%  the context behaviour is expressed recursively and no be expressed recursively. 
Also, entity mutations can be expressed easily and different reaction systems can
communicate between them.

@@

We believe that our embedding can contribute to extend the applications
of Reaction Systems to diverse fields of computer science, and life
sciences.

@@

We believe that our work can also help to extend the framework
of RSs towards a model which can improve the communication
between different RSs.

>>>>

In this paper we have introduced c\CNA, a variant of the {\tt link}-calculus
where prefixes are link chains and no more single links, as it was 
briefly described in the future work section in~\cite{BBB17}.
This variant allowed us to define 
%shown 
a faithful embedding of Reaction Systems,
an emerging formalism to model computationally biochemical systems.
%into multilink processes.  
This translation shows several benefits.
For instance, in our paper the context of a RS can work non deterministically and it 
is recursively defined.
%  the context behaviour is expressed recursively and no be expressed recursively. 
Also, entity mutations can be expressed easily and different reaction systems can
communicate between them.

@@

We are confident that our embedding can contribute to extend the applications
of Reaction Systems to diverse fields of computer science, and life
sciences.

@@

We also plan to build on the work in this paper to extend the framework
of RSs towards a model where different RSs are allowed to communicate.
